Surface programmable materials

### 2024-08-22 paper/main.tex
added picture of model

\usepackage{svg}
\usepackage{amsmath}
\usepackage{graphicx}% Include figure files
\usepackage{textcomp}
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{mathrsfs}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{txfonts}
\usepackage{algorithm}  
\usepackage{algpseudocode}  
\usepackage{balance}
\usepackage{flushend}
\usepackage{cleveref}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm

@@

>>>>

\usepackage{svg}
\usepackage{amsmath}
\usepackage{graphicx}% Include figure files
\usepackage{textcomp}
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{mathrsfs}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{txfonts}
\usepackage{algorithm}  
\usepackage{algpseudocode}  
\usepackage{balance}
\usepackage{flushend}
\usepackage{cleveref}
\usepackage{tikz}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm

@@

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{center}
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Square [id:dp3257799447745866] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (30,30) -- (40,30) -- (40,54) -- (30,54) -- cycle ;
%Straight Lines [id:da8913459345633652] 
\draw    (20,42) -- (30,42) ;
%Straight Lines [id:da9790784501640646] 
\draw    (40,42) -- (60,42) ;
%Shape: Square [id:dp5326406990508012] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (70,30) -- (80,30) -- (80,54) -- (70,54) -- cycle ;
%Straight Lines [id:da008320062158621688] 
\draw    (80,42) -- (100,42) ;
%Shape: Square [id:dp29003962631292124] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (30,60) -- (40,60) -- (40,84) -- (30,84) -- cycle ;
%Straight Lines [id:da8695035786947396] 
\draw    (20,72) -- (30,72) ;
%Straight Lines [id:da417768427429108] 
\draw    (40,72) -- (60,72) ;
%Shape: Square [id:dp08018354727485644] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (70,60) -- (80,60) -- (80,84) -- (70,84) -- cycle ;
%Straight Lines [id:da7038299022670145] 
\draw    (80,72) -- (100,72) ;
%Shape: Square [id:dp4665291997770109] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (30,90) -- (40,90) -- (40,114) -- (30,114) -- cycle ;
%Straight Lines [id:da9280920191618629] 
\draw    (20,102) -- (30,102) ;
%Straight Lines [id:da023978392575592755] 
\draw    (40,102) -- (60,102) ;
%Shape: Square [id:dp9172017959293151] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (70,90) -- (80,90) -- (80,114) -- (70,114) -- cycle ;
%Straight Lines [id:da515300595667447] 
\draw    (80,102) -- (100,102) ;
%Straight Lines [id:da9288304396586808] 
\draw    (80,72) -- (100,72) ;
%Straight Lines [id:da852280866297966] 
\draw    (80,102) -- (100,102) ;
%Shape: Square [id:dp32738689596333903] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (30,160) -- (40,160) -- (40,184) -- (30,184) -- cycle ;
%Straight Lines [id:da07485978922844372] 
\draw    (20,172) -- (30,172) ;
%Straight Lines [id:da2475700164417307] 
\draw    (40,172) -- (60,172) ;
%Shape: Square [id:dp4553302503149699] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (70,160) -- (80,160) -- (80,184) -- (70,184) -- cycle ;
%Straight Lines [id:da5669313532997795] 
\draw    (80,172) -- (100,172) ;
%Shape: Square [id:dp681519742049937] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (163,30) -- (173,30) -- (173,54) -- (163,54) -- cycle ;
%Shape: Square [id:dp2901897648605303] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (163,60) -- (173,60) -- (173,84) -- (163,84) -- cycle ;
%Shape: Square [id:dp9710219091133365] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (163,90) -- (173,90) -- (173,114) -- (163,114) -- cycle ;
%Shape: Square [id:dp47295881968788644] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (163,160) -- (173,160) -- (173,184) -- (163,184) -- cycle ;
%Straight Lines [id:da1585638759400958] 
\draw    (173,172) -- (183,172) ;
%Straight Lines [id:da5795532995572801] 
\draw    (173,102) -- (183,102) ;
%Straight Lines [id:da8448651727682703] 
\draw    (173,72) -- (183,72) ;
%Straight Lines [id:da9060816552835422] 
\draw    (173,42) -- (183,42) ;
%Shape: Circle [id:dp818609500871543] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,42) .. controls (42,40.34) and (43.34,39) .. (45,39) .. controls (46.66,39) and (48,40.34) .. (48,42) .. controls (48,43.66) and (46.66,45) .. (45,45) .. controls (43.34,45) and (42,43.66) .. (42,42) -- cycle ;
%Shape: Circle [id:dp13831345755639668] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,72) .. controls (42,70.34) and (43.34,69) .. (45,69) .. controls (46.66,69) and (48,70.34) .. (48,72) .. controls (48,73.66) and (46.66,75) .. (45,75) .. controls (43.34,75) and (42,73.66) .. (42,72) -- cycle ;
%Shape: Circle [id:dp9041445092942773] 
\draw   (42,102) .. controls (42,100.34) and (43.34,99) .. (45,99) .. controls (46.66,99) and (48,100.34) .. (48,102) .. controls (48,103.66) and (46.66,105) .. (45,105) .. controls (43.34,105) and (42,103.66) .. (42,102) -- cycle ;
%Shape: Circle [id:dp7529245942690144] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,172) .. controls (42,170.34) and (43.34,169) .. (45,169) .. controls (46.66,169) and (48,170.34) .. (48,172) .. controls (48,173.66) and (46.66,175) .. (45,175) .. controls (43.34,175) and (42,173.66) .. (42,172) -- cycle ;
%Shape: Circle [id:dp4421700288524639] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,172) .. controls (82,170.34) and (83.34,169) .. (85,169) .. controls (86.66,169) and (88,170.34) .. (88,172) .. controls (88,173.66) and (86.66,175) .. (85,175) .. controls (83.34,175) and (82,173.66) .. (82,172) -- cycle ;
%Shape: Circle [id:dp4431783957619826] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,102) .. controls (82,100.34) and (83.34,99) .. (85,99) .. controls (86.66,99) and (88,100.34) .. (88,102) .. controls (88,103.66) and (86.66,105) .. (85,105) .. controls (83.34,105) and (82,103.66) .. (82,102) -- cycle ;
%Shape: Circle [id:dp403539897070186] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,102) .. controls (42,100.34) and (43.34,99) .. (45,99) .. controls (46.66,99) and (48,100.34) .. (48,102) .. controls (48,103.66) and (46.66,105) .. (45,105) .. controls (43.34,105) and (42,103.66) .. (42,102) -- cycle ;
%Shape: Circle [id:dp8783887479009327] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,72) .. controls (82,70.34) and (83.34,69) .. (85,69) .. controls (86.66,69) and (88,70.34) .. (88,72) .. controls (88,73.66) and (86.66,75) .. (85,75) .. controls (83.34,75) and (82,73.66) .. (82,72) -- cycle ;
%Shape: Circle [id:dp6224124506773947] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,42) .. controls (82,40.34) and (83.34,39) .. (85,39) .. controls (86.66,39) and (88,40.34) .. (88,42) .. controls (88,43.66) and (86.66,45) .. (85,45) .. controls (83.34,45) and (82,43.66) .. (82,42) -- cycle ;
%Shape: Circle [id:dp8043981259851258] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (175,102) .. controls (175,100.34) and (176.34,99) .. (178,99) .. controls (179.66,99) and (181,100.34) .. (181,102) .. controls (181,103.66) and (179.66,105) .. (178,105) .. controls (176.34,105) and (175,103.66) .. (175,102) -- cycle ;
%Shape: Circle [id:dp43816466417546707] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (175,172) .. controls (175,170.34) and (176.34,169) .. (178,169) .. controls (179.66,169) and (181,170.34) .. (181,172) .. controls (181,173.66) and (179.66,175) .. (178,175) .. controls (176.34,175) and (175,173.66) .. (175,172) -- cycle ;
%Shape: Circle [id:dp5620143122025991] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (175,72) .. controls (175,70.34) and (176.34,69) .. (178,69) .. controls (179.66,69) and (181,70.34) .. (181,72) .. controls (181,73.66) and (179.66,75) .. (178,75) .. controls (176.34,75) and (175,73.66) .. (175,72) -- cycle ;
%Shape: Circle [id:dp8865997979090963] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (175,42) .. controls (175,40.34) and (176.34,39) .. (178,39) .. controls (179.66,39) and (181,40.34) .. (181,42) .. controls (181,43.66) and (179.66,45) .. (178,45) .. controls (176.34,45) and (175,43.66) .. (175,42) -- cycle ;
%Shape: Circle [id:dp18306264726647137] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,202) .. controls (42,200.34) and (43.34,199) .. (45,199) .. controls (46.66,199) and (48,200.34) .. (48,202) .. controls (48,203.66) and (46.66,205) .. (45,205) .. controls (43.34,205) and (42,203.66) .. (42,202) -- cycle ;
%Shape: Circle [id:dp3243993178712161] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,12) .. controls (42,10.34) and (43.34,9) .. (45,9) .. controls (46.66,9) and (48,10.34) .. (48,12) .. controls (48,13.66) and (46.66,15) .. (45,15) .. controls (43.34,15) and (42,13.66) .. (42,12) -- cycle ;
%Shape: Circle [id:dp3529141461836287] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,12) .. controls (135,10.34) and (136.34,9) .. (138,9) .. controls (139.66,9) and (141,10.34) .. (141,12) .. controls (141,13.66) and (139.66,15) .. (138,15) .. controls (136.34,15) and (135,13.66) .. (135,12) -- cycle ;
%Shape: Circle [id:dp9431375452836528] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,202) .. controls (135,200.34) and (136.34,199) .. (138,199) .. controls (139.66,199) and (141,200.34) .. (141,202) .. controls (141,203.66) and (139.66,205) .. (138,205) .. controls (136.34,205) and (135,203.66) .. (135,202) -- cycle ;
%Straight Lines [id:da9696356596865732] 
\draw    (5,42) -- (20,42) ;
%Straight Lines [id:da5317592058087168] 
\draw    (5,72) -- (20,72) ;
%Straight Lines [id:da6169293205402535] 
\draw    (5,102) -- (20,102) ;
%Straight Lines [id:da9653690034485647] 
\draw    (5,172) -- (20,172) ;
%Shape: Circle [id:dp11541023046031418] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,42) .. controls (2,40.34) and (3.34,39) .. (5,39) .. controls (6.66,39) and (8,40.34) .. (8,42) .. controls (8,43.66) and (6.66,45) .. (5,45) .. controls (3.34,45) and (2,43.66) .. (2,42) -- cycle ;
%Shape: Circle [id:dp9967907554667488] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,72) .. controls (2,70.34) and (3.34,69) .. (5,69) .. controls (6.66,69) and (8,70.34) .. (8,72) .. controls (8,73.66) and (6.66,75) .. (5,75) .. controls (3.34,75) and (2,73.66) .. (2,72) -- cycle ;
%Shape: Circle [id:dp5466737045582317] 
\draw   (2,102) .. controls (2,100.34) and (3.34,99) .. (5,99) .. controls (6.66,99) and (8,100.34) .. (8,102) .. controls (8,103.66) and (6.66,105) .. (5,105) .. controls (3.34,105) and (2,103.66) .. (2,102) -- cycle ;
%Shape: Circle [id:dp22351697734701603] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,172) .. controls (2,170.34) and (3.34,169) .. (5,169) .. controls (6.66,169) and (8,170.34) .. (8,172) .. controls (8,173.66) and (6.66,175) .. (5,175) .. controls (3.34,175) and (2,173.66) .. (2,172) -- cycle ;
%Shape: Circle [id:dp07423205757027329] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,102) .. controls (2,100.34) and (3.34,99) .. (5,99) .. controls (6.66,99) and (8,100.34) .. (8,102) .. controls (8,103.66) and (6.66,105) .. (5,105) .. controls (3.34,105) and (2,103.66) .. (2,102) -- cycle ;
%Shape: Circle [id:dp44591669371444054] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,202) .. controls (2,200.34) and (3.34,199) .. (5,199) .. controls (6.66,199) and (8,200.34) .. (8,202) .. controls (8,203.66) and (6.66,205) .. (5,205) .. controls (3.34,205) and (2,203.66) .. (2,202) -- cycle ;
%Shape: Circle [id:dp8124810079347506] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,12) .. controls (2,10.34) and (3.34,9) .. (5,9) .. controls (6.66,9) and (8,10.34) .. (8,12) .. controls (8,13.66) and (6.66,15) .. (5,15) .. controls (3.34,15) and (2,13.66) .. (2,12) -- cycle ;
%Curve Lines [id:da6837659640523519] 
\draw    (12,72) .. controls (11.9,72.82) and (16.25,48.02) .. (30,48) ;
%Curve Lines [id:da14157714470554095] 
\draw    (12,102) .. controls (12.25,102.02) and (16.25,78.02) .. (30,78) ;
%Curve Lines [id:da29397752720095016] 
\draw    (10,132) .. controls (9.9,131.92) and (16.25,108.02) .. (30,108) ;
%Curve Lines [id:da1010168964172955] 
\draw    (8,202) .. controls (7.88,201.94) and (16.25,178.02) .. (30,178) ;
%Curve Lines [id:da41907939317602727] 
\draw    (30,66) .. controls (15.95,66.07) and (11.95,42.82) .. (12,42) ;
%Curve Lines [id:da4960426207730133] 
\draw    (30,96) .. controls (15.95,96.07) and (11.95,72.82) .. (12,72) ;
%Curve Lines [id:da32194834856252696] 
\draw    (30,126) .. controls (15.95,126.07) and (11.95,102.82) .. (12,102) ;
%Curve Lines [id:da9942559529163806] 
\draw    (30,166) .. controls (15.95,166.07) and (9.95,142.82) .. (10,142) ;
%Curve Lines [id:da30812169087400987] 
\draw    (30,36) .. controls (15.95,36.07) and (7.95,12.82) .. (8,12) ;
%Curve Lines [id:da7415436207281032] 
\draw    (12,172) .. controls (12.4,171.42) and (16.25,148.02) .. (30,148) ;
%Straight Lines [id:da945225908298071] 
\draw    (59.5,42) -- (69.5,42) ;
%Straight Lines [id:da019486859954932045] 
\draw    (59.5,72) -- (69.5,72) ;
%Straight Lines [id:da10691701544026788] 
\draw    (59.5,102) -- (69.5,102) ;
%Straight Lines [id:da08190608552147682] 
\draw    (59.5,172) -- (69.5,172) ;
%Straight Lines [id:da5383715063718815] 
\draw    (48,42) -- (59.5,42) ;
%Straight Lines [id:da29185686612996165] 
\draw    (48,72) -- (59.5,72) ;
%Straight Lines [id:da6312076314118666] 
\draw    (48,102) -- (59.5,102) ;
%Straight Lines [id:da0122276432828059] 
\draw    (48,172) -- (59.5,172) ;
%Curve Lines [id:da634843349549117] 
\draw    (51.5,72) .. controls (51.4,72.82) and (55.75,48.02) .. (69.5,48) ;
%Curve Lines [id:da29334484540724026] 
\draw    (51.5,102) .. controls (51.75,102.02) and (55.75,78.02) .. (69.5,78) ;
%Curve Lines [id:da3089090169112314] 
\draw    (49.5,132) .. controls (49.4,131.92) and (55.75,108.02) .. (69.5,108) ;
%Curve Lines [id:da24605443838188257] 
\draw    (47.5,202) .. controls (47.38,201.94) and (55.75,178.02) .. (69.5,178) ;
%Curve Lines [id:da497728473744927] 
\draw    (69.5,66) .. controls (55.45,66.07) and (51.45,42.82) .. (51.5,42) ;
%Curve Lines [id:da1733603989545598] 
\draw    (69.5,96) .. controls (55.45,96.07) and (51.45,72.82) .. (51.5,72) ;
%Curve Lines [id:da7391016400644088] 
\draw    (69.5,126) .. controls (55.45,126.07) and (51.45,102.82) .. (51.5,102) ;
%Curve Lines [id:da2610882313501728] 
\draw    (69.5,166) .. controls (55.45,166.07) and (49.45,142.82) .. (49.5,142) ;
%Curve Lines [id:da9723708662465751] 
\draw    (69.5,36) .. controls (55.45,36.07) and (47.45,12.82) .. (47.5,12) ;
%Curve Lines [id:da7225849641270694] 
\draw    (51.5,172) .. controls (51.9,171.42) and (55.75,148.02) .. (69.5,148) ;
%Straight Lines [id:da7791377752665631] 
\draw    (100,42) -- (110,42) ;
%Straight Lines [id:da23522073116206266] 
\draw    (100,72) -- (110,72) ;
%Straight Lines [id:da18218908732788264] 
\draw    (100,102) -- (110,102) ;
%Straight Lines [id:da3309320538017131] 
\draw    (100,172) -- (110,172) ;
%Straight Lines [id:da4610992726495633] 
\draw    (88,42) -- (100,42) ;
%Straight Lines [id:da1358122827839865] 
\draw    (88,72) -- (100,72) ;
%Straight Lines [id:da9749891373044985] 
\draw    (88,102) -- (100,102) ;
%Straight Lines [id:da6902822758606824] 
\draw    (88,172) -- (100,172) ;
%Curve Lines [id:da8937700604447827] 
\draw    (92,72) .. controls (91.9,72.82) and (96.25,48.02) .. (110,48) ;
%Curve Lines [id:da3731849249187291] 
\draw    (92,102) .. controls (92.25,102.02) and (96.25,78.02) .. (110,78) ;
%Curve Lines [id:da9742316406042617] 
\draw    (88,202) .. controls (87.88,201.94) and (96.25,178.02) .. (110,178) ;
%Curve Lines [id:da6734623491912421] 
\draw    (110,66) .. controls (95.95,66.07) and (91.95,42.82) .. (92,42) ;
%Curve Lines [id:da9728942718366658] 
\draw    (110,96) .. controls (95.95,96.07) and (91.95,72.82) .. (92,72) ;
%Curve Lines [id:da5314963895208473] 
\draw    (110,126) .. controls (95.95,126.07) and (91.95,102.82) .. (92,102) ;
%Curve Lines [id:da20527729986926668] 
\draw    (110,36) .. controls (95.95,36.07) and (87.95,12.82) .. (88,12) ;
%Curve Lines [id:da9357477032373158] 
\draw    (92,172) .. controls (92.4,171.42) and (96.25,148.02) .. (110,148) ;
%Shape: Circle [id:dp03524070526370693] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,12) .. controls (82,10.34) and (83.34,9) .. (85,9) .. controls (86.66,9) and (88,10.34) .. (88,12) .. controls (88,13.66) and (86.66,15) .. (85,15) .. controls (83.34,15) and (82,13.66) .. (82,12) -- cycle ;
%Shape: Circle [id:dp5282167504002355] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,202) .. controls (82,200.34) and (83.34,199) .. (85,199) .. controls (86.66,199) and (88,200.34) .. (88,202) .. controls (88,203.66) and (86.66,205) .. (85,205) .. controls (83.34,205) and (82,203.66) .. (82,202) -- cycle ;
%Straight Lines [id:da28818147273527717] 
\draw    (133.6,41.96) -- (153.6,41.96) ;
%Straight Lines [id:da4792679687432131] 
\draw    (133.6,71.96) -- (153.6,71.96) ;
%Straight Lines [id:da2794298478395634] 
\draw    (133.6,101.96) -- (153.6,101.96) ;
%Straight Lines [id:da610925391950311] 
\draw    (133.6,171.96) -- (153.6,171.96) ;
%Straight Lines [id:da31436080279800227] 
\draw    (153.1,41.96) -- (163.1,41.96) ;
%Straight Lines [id:da07642255702447143] 
\draw    (153.1,71.96) -- (163.1,71.96) ;
%Straight Lines [id:da48431709040149795] 
\draw    (153.1,101.96) -- (163.1,101.96) ;
%Straight Lines [id:da31077160308421736] 
\draw    (153.1,171.96) -- (163.1,171.96) ;
%Straight Lines [id:da4482666583263508] 
\draw    (141.6,41.96) -- (153.1,41.96) ;
%Straight Lines [id:da0031324911441572567] 
\draw    (141.6,71.96) -- (153.1,71.96) ;
%Straight Lines [id:da39186514465416056] 
\draw    (141.6,101.96) -- (153.1,101.96) ;
%Straight Lines [id:da9984443909601395] 
\draw    (141.6,171.96) -- (153.1,171.96) ;
%Curve Lines [id:da2794596982451869] 
\draw    (145.1,71.96) .. controls (145,72.79) and (149.35,47.99) .. (163.1,47.96) ;
%Curve Lines [id:da5527279625811088] 
\draw    (145.1,101.96) .. controls (145.35,101.99) and (149.35,77.99) .. (163.1,77.96) ;
%Curve Lines [id:da49469050221037403] 
\draw    (143.1,131.96) .. controls (143,131.89) and (149.35,107.99) .. (163.1,107.96) ;
%Curve Lines [id:da5889227861048327] 
\draw    (141.1,201.96) .. controls (140.98,201.9) and (149.35,177.99) .. (163.1,177.96) ;
%Curve Lines [id:da046574817758556986] 
\draw    (163.1,65.96) .. controls (149.05,66.04) and (145.05,42.79) .. (145.1,41.96) ;
%Curve Lines [id:da2878436840249363] 
\draw    (163.1,95.96) .. controls (149.05,96.04) and (145.05,72.79) .. (145.1,71.96) ;
%Curve Lines [id:da49553051429298844] 
\draw    (163.1,125.96) .. controls (149.05,126.04) and (145.05,102.79) .. (145.1,101.96) ;
%Curve Lines [id:da6292297348811737] 
\draw    (163.1,165.96) .. controls (149.05,166.04) and (143.05,142.79) .. (143.1,141.96) ;
%Curve Lines [id:da8001909344877356] 
\draw    (163.1,35.96) .. controls (149.05,36.04) and (141.05,12.79) .. (141.1,11.96) ;
%Curve Lines [id:da549670443628927] 
\draw    (145.1,171.96) .. controls (145.5,171.39) and (149.35,147.99) .. (163.1,147.96) ;
%Shape: Circle [id:dp3208676418353624] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,42) .. controls (135,40.34) and (136.34,39) .. (138,39) .. controls (139.66,39) and (141,40.34) .. (141,42) .. controls (141,43.66) and (139.66,45) .. (138,45) .. controls (136.34,45) and (135,43.66) .. (135,42) -- cycle ;
%Shape: Circle [id:dp3190617032943761] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,72) .. controls (135,70.34) and (136.34,69) .. (138,69) .. controls (139.66,69) and (141,70.34) .. (141,72) .. controls (141,73.66) and (139.66,75) .. (138,75) .. controls (136.34,75) and (135,73.66) .. (135,72) -- cycle ;
%Shape: Circle [id:dp5981517901086082] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,102) .. controls (135,100.34) and (136.34,99) .. (138,99) .. controls (139.66,99) and (141,100.34) .. (141,102) .. controls (141,103.66) and (139.66,105) .. (138,105) .. controls (136.34,105) and (135,103.66) .. (135,102) -- cycle ;
%Shape: Circle [id:dp9782081274652843] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,172) .. controls (135,170.34) and (136.34,169) .. (138,169) .. controls (139.66,169) and (141,170.34) .. (141,172) .. controls (141,173.66) and (139.66,175) .. (138,175) .. controls (136.34,175) and (135,173.66) .. (135,172) -- cycle ;

% Text Node
\draw (108,33) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
% Text Node
\draw (108,63) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
% Text Node
\draw (108,93.29) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
% Text Node
\draw (108,163) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
% Text Node
\draw (160,127.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
% Text Node
\draw (17,127.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
% Text Node
\draw (56.5,127.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
% Text Node
\draw (97,127.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
% Text Node
\draw (150.1,127.13) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};

\end{tikzpicture}
\end{center}
